# Introduction

## Background
Accurate BP measurement remains a cornerstone in the diagnosis of hypertension, the evaluation of cardiovascular risk, and the management of therapeutic strategies. Although measurement technologies have advanced significantly over the past decades, the pursuit of a method that is universally accurate, reliable, and feasible in various clinical settings is still ongoing.
For more than a century, the auscultatory method using a mercury sphygmomanometer has been recognized as the gold standard for non-invasive blood pressure (BP) measurement in clinical settings1. This method entails the inflation of an arm cuff to occlude arterial blood flow-most commonly in the brachial artery-followed by gradual deflation while a trained observer detects Korotkoff sounds(K-sounds) via stethoscope(Figure 1.1). The onset of the first K-sound (phase I) is interpreted as the systolic blood pressure (SBP), whereas the disappearance of the sounds (phase V) typically marks the diastolic blood pressure (DBP)(Table 1)2. The K-sounds are characterized by five distinct phases: Phase I (clear tapping), Phase II (swooshing sounds or murmurs), Phase III (crisper, more intense tapping), Phase IV (abrupt muffling of sounds), and Phase V (silence, or the disappearance of sounds). Accurate identification of these phases, particularly I and V (or IV in certain populations), is paramount for correct BP assessment. The durability, straightforward design, and high inter-device consistency of mercury sphygmomanometers across manufacturers have all contributed to their longstanding acceptance and reliability in clinical practice. 
Manual blood pressure measurement using K-sound is subject to several limitations, primarily related to human error and observer variability2. Inaccurate cuff or stethoscope placement, difficulty detecting faint sounds due to noise or inattention, and inconsistencies in identifying the precise pressure at which sounds appear or disappear can all compromise accuracy. Studies have shown that even small changes in stethoscope positioning can lead to significant variations in readings3. Inter-observer variability further reduces reliability, as differences in technique, experience, and hearing acuity can result in inconsistent measurements from the same patient.
Environmental factors also affect measurement quality. Background noise, common in clinical settings, can obscure K-sounds, especially the softer Phase I and V sounds. In addition, while often considered straightforward, manual BP measurement requires careful technique and proper training. It is time-consuming and may not be practical in high-volume or emergency care settings, where speed and consistency are critical.
Despite these challenges, the mercury sphygmomanometer remains particularly valuable when clinical decisions are based on precise blood pressure readings, as the method provides unparalleled accuracy when performed correctly. 



```{r fig.cap="Figure 1.1. BP measurement by auscultatory method. An inflatable upper-arm cuff is inflated to occlude the brachial artery and then slowly deflated while Korotkoff sounds are detected with a stethoscope placed over the artery. The appearance of the first Korotkoff sound during deflation indicates systolic blood pressure, and the disappearance of Korotkoff sounds indicates diastolic blood pressure."}
fig11_path_candidates <- c(
  "output/figure/external/1-1.png",
  "output/figures/External/1-1.png",
  "outputs/figures/External/1-1.png",
  "../output/figure/external/1-1.png",
  "../output/figures/External/1-1.png",
  "../outputs/figures/External/1-1.png"
)
fig11_path <- fig11_path_candidates[file.exists(fig11_path_candidates)][1]
if (is.na(fig11_path)) {
  stop(
    "'1-1.png' not found. Checked:\n",
    paste(fig11_path_candidates, collapse = "\n")
  )
}
knitr::include_graphics(fig11_path)
```

Table 1. Korotkoff Sound Phases

| Phase | Qualitative description |
|---|---|
| I | Appearance: The first loud tapping sound heard; systolic pressure |
| II | Softening: Weakened clapping sound and soft wind-like murmur |
| III | Sharpening: Blowing wind-like murmur disappears |
| IV | Muffling: The tone is suddenly dull |
| V | Disappearance: Loss of sound; diastolic pressure |

## Oscillometric Method Principles and Limitations

### Fundamental mechanisms
The inherent limitations and practical inconveniences of auscultatory blood pressure measurement have naturally led to the emergence of automated blood pressure monitoring technologies. Among these, oscillometric devices have become the most widely used form of automated blood pressure monitors in clinical and home settings. The widespread adoption of automated oscillometric blood pressure monitors has fundamentally transformed clinical practice, offering convenience, standardization, and reduced dependence on operator skill4. Similar to the auscultatory method, the oscillometric technique also requires the use of an inflatable cuff placed on the upper arm to occlude arterial blood flow. As the cuff gradually deflates and the pressure falls below the SBP, blood flow resumes intermittently. These intermittent flows cause the arterial wall beneath the cuff to expand and contract with each cardiac cycle. The resulting arterial wall movements generate pulsations that are transmitted to the air within the cuff, producing small, superimposed pressure oscillations. These oscillations serve as the primary signal detected by the device's internal pressure sensor, which typically consists of a piezoresistive silicon transducer5. 

The sensor detects raw signals composed of gradually declining cuff pressure overlaid with small pressure oscillations generated by arterial pulsations. These signals undergo filtering to remove low-frequency baseline drift and high-frequency noise, followed by amplification to enhance the oscillometric waveform (OMW). From the processed OMW, an oscillometric pulse index (OPI) is calculated for each cardiac cycle-commonly defined by parameters such as peak-to-peak amplitude or area under the pulse. Plotting OPI values against corresponding cuff pressures yields the oscillometric waveform envelope (OMWE)6, which is often smoothed using curve-fitting methods. A key principle in this approach is the Maximum Amplitude Algorithm (MAA), which identifies the cuff pressure at the peak of the OMWE as the mean arterial pressure (MAP)6. This peak corresponds to the point where cuff pressure equals intra-arterial pressure, resulting in maximal arterial wall oscillation. As such, MAP is generally regarded as the most accurate parameter derived from oscillometric measurements.

Unlike MAP, SBP and DBP are not directly identified by a unique, universally agreed-upon feature of the OMWE. Instead, they are estimated or calculated based on the characteristics of the OMWE, often in relation to the already determined MAP, using proprietary algorithms that vary between device manufacturers4. 


```{r fig.cap="Figure 1.2. BP measurement of oscillometric method. An upper-arm cuff is inflated above arterial occlusion pressure and then gradually deflated. During deflation, arterial volume changes induce pressure oscillations that are superimposed on the cuff pressure signal (oscillometric waveform). The oscillation amplitude increases as cuff pressure approaches MAP and then decreases. SBP and DBP are estimated from the envelope using device-specific algorithms."}
fig12_path_candidates <- c(
  "output/figure/external/1-2.png",
  "output/figures/External/1-2.png",
  "outputs/figures/External/1-2.png",
  "../output/figure/external/1-2.png",
  "../output/figures/External/1-2.png",
  "../outputs/figures/External/1-2.png"
)
fig12_path <- fig12_path_candidates[file.exists(fig12_path_candidates)][1]
if (is.na(fig12_path)) {
  stop(
    "'1-2.png' not found. Checked:\n",
    paste(fig12_path_candidates, collapse = "\n")
  )
}
knitr::include_graphics(fig12_path)
```
### Systematic Limitations and Accuracy Concerns 
The oscillometric method operates on the principle of detecting pressure oscillations within the arterial wall during controlled cuff deflation, utilizing maximum amplitude algorithms to determine blood pressure values4. Unlike auscultatory methods that rely on auditory detection of K-sounds, oscillometric devices measure the amplitude of pressure oscillations transmitted through the arterial wall to the cuff7. The algorithm identifies the cuff pressure corresponding to maximum oscillation amplitude as the mean arterial pressure, while SBP and DBP are calculated using predetermined ratios. This automated approach eliminates observer variability and provides consistent measurement protocols, making it particularly attractive for standardized clinical applications. However, the reliance on algorithmic interpretation of pressure oscillations introduces specific limitations that affect measurement accuracy in patients with altered vascular mechanics7. These algorithms, which dictate how MAP is precisely identified and how SBP and DBP are subsequently derived from the OMWE, are typically considered trade secrets by manufacturers and are not publicly disclosed for independent critique or validation. This lack of transparency, often referred to as the "black box" issue, presents several critical challenges. It prevents a clear understanding of why different devices may yield inconsistent readings for the same patient, complicates efforts to assess the impact of specific physiological conditions such as increased arterial stiffness or atrial fibrillation, and obstructs the development of standardized correction methods to improve measurement reliability across diverse populations and devices. Moreover, because these algorithms are often developed using data from individuals with presumed normal cardiovascular profiles, their accuracy may be compromised in patients with abnormal hemodynamics. As a result, the reliance on algorithmic inference rather than direct physiological measurement remains a fundamental source of error and uncertainty. 

In a study of 337 cardiology outpatients, BP was measured simultaneously using both a mercury manometer and an automated oscillometric device. Mercury readings were significantly higher than oscillometric values for both systolic and diastolic pressures (p < 0.0001), with discrepancies seen in over 20% of patients. The average differences were 1.95 mmHg (systolic) and 1.3 mmHg (diastolic), with greater discrepancies observed in patients over 658. A meta-analysis comparing oscillometric readings to invasive arterial pressure found that while mean arterial pressure showed a small average bias of -1.50 mmHg, the limits of agreement were wide (from -14.6 mmHg to +40.3 mmHg)9. Such variability reduces the reliability of oscillometric methods in clinical situations where precise blood pressure control is essential. 

### Issues in Atherosclerotic Cardiovascular Disease
Atherosclerotic cardiovascular disease (ASCVD) significantly alters arterial wall mechanics, thereby compromising the accuracy of oscillometric blood pressure (BP) measurements. Arterial stiffening, a hallmark of ASCVD, results primarily from wall thickening and elastin degeneration-each contributing differently to measurement error. As arterial stiffness increases, the characteristics of the arterial pressure wave are altered, subsequently affecting the amplitude and shape of cuff pressure oscillations10. In individuals with compliant arteries, the peak of the OMWE is typically well-defined and narrow. However, in older adults or patients with stiffened arteries-conditions often accompanied by a widened pulse pressure-the OMWE peak becomes broader and flatter. Since SBP and DBP are derived algorithmically from the OMWE in reference to the identified MAP, such morphological changes in the envelope inevitably introduce inaccuracies in the estimation of SBP and DBP.11
Wall thickening is associated with overestimation of SBP, whereas elastin degeneration affects both SBP and DBP7 12. In advanced stages of ASCVD, especially among patients with diabetes or end-stage renal disease, extensive arterial calcification further complicates measurement. Calcified vessels become rigid and poorly compressible, limiting the cuff's ability to fully occlude the artery or detect oscillometric signals accurately, thus exacerbating measurement inaccuracy13. Insights from computational modeling have elucidated that such structural changes in the arterial wall markedly affect pressure transmission dynamics during cuff inflation and deflation, thereby compromising the reliability of oscillometric readings7. These findings are consistent with clinical observations of pseudo-hypertension in elderly individuals with advanced atherosclerosis, where heightened arterial stiffness requires greater external cuff pressure to achieve arterial occlusion, thereby leading to falsely elevated blood pressure measurements. The clinical implications of these inaccuracies are substantial, as they may lead to overdiagnosis of hypertension and unwarranted therapeutic interventions. A simulation study14 further supports these concerns by demonstrating that arterial stiffening-characterized by changes in the symmetry and steepness of the artery-cuff pressure/volume relationship-can induce substantial errors in oscillometric BP estimation. Their findings showed that SBP errors could reach up to +11.6 mmHg, while diastolic errors varied from over- to underestimation depending on the combination of arterial compliance parameters. Notably, mean arterial pressure errors were the most variable, with deviations as large as ±17.5 mmHg. These errors were strongly influenced by pulse pressure and the mismatch between the arterial pulse shape index and the cuff pressure/volume symmetry index, emphasizing the complexity and vulnerability of oscillometric estimation algorithms in the presence of altered arterial mechanics.
The impact of atherosclerosis on oscillometric accuracy extends beyond individual variability and carries implications for broader patient populations. Evidence from studies investigating arterial stiffness indices suggests that conventional compliance assessments under physiologic pressure ranges may be insufficient to predict oscillometric accuracy in patients with marked vascular pathology. Accordingly, there is an urgent need to develop alternative BP assessment modalities or calibration strategies in populations with elevated cardiovascular risk and structural vascular abnormalities.

### Specific Problems in Atrial Fibrillation Patients
Atrial fibrillation(AF) presents unique challenges for oscillometric BP measurement due to the inherent irregularity of cardiac rhythm and stroke volume variation15. The hallmark of AF is a chaotic and irregular atrial activity, resulting in an irregularly irregular ventricular response. This irregularity in ventricular contractions leads to marked beat-to-beat variations in ventricular filling time and stroke volume. Consequently, there is substantial beat-to-beat variability in both SBP and DBP. Studies quantifying this variability have shown that, compared to individuals in sinus rhythm (SR), patients with AF exhibit approximately a doubling of SBP variability and a six-fold increase in diastolic BP variability16. The oscillometric method relies on consistent pressure oscillations for accurate algorithmic interpretation, but atrial fibrillation introduces significant beat-to-beat variability that can confound measurement accuracy17. The accuracy of oscillometric BP measurement in AF is not uniform across all devices. Significant discrepancies exist among different validation studies. Pagonas et al.18 studied the Omron M5 Professional (upper arm) and R5 Professional (wrist) devices against invasive arterial pressure. They concluded that if three consecutive measurements were averaged, AF did not significantly affect the mean bias of SBP and DBP. However, they did find that the within-subject variability of oscillometric measurements was significantly higher in patients with AF compared to those in sinus rhythm. Another study19 using the Microlife BP A6 PC (which has an AF detection system) found that, compared to the auscultatory method, the device reported SBP values that were on average 5.3 mmHg higher in SR patients and 6.1 mmHg higher in AF patients. While the mean differences were relatively small, the limits of agreement were very wide ( -23.9 to 11.7 mmHg for SBP in AF), indicating poor individual reliability. Feenstra et al.17 compared two oscillometric devices-the Welch Allyn Spot Vital Signs (WASVS) and Philips M3002A IntelliVue X2-against the Volume Clamp Method (VCM) in patients with atrial fibrillation (AF). The WASVS showed deviations of +0.1±14.8mmHg for SBP and +6.3±9.2mmHg for DBP, while the Philips device showed 6.8±13.2mmHg for SBP and +9.4±8.1mmHg for DBP. Notably, high beat-to-beat variability and elevated heart rate reduced the accuracy of the WASVS. The study concluded that oscillometric BP measurement in AF is generally limited in accuracy and may be unreliable in individual cases. Accordingly, oscillometric BP values obtained in AF should be interpreted as estimates whose accuracy depends on the specific device and the measurement conditions; clinicians should therefore interpret these readings with caution rather than treating them as interchangeable physiologic truth.




Table 2 presents a comparison of the strengths and limitations of the two blood pressure measurement methods.

Table 2. Comparative overview of Sphygmomanometer Technologies

| Type | Advantages | Limitations | Validation status |
|---|---|---|---|
| Manual auscultatory | Gold standard; simple design; consistent across manufacturers. | Environmental toxicity of mercury leading to phase-out; requires trained observer; susceptible to observer bias. | Well-established |
| Automated oscillometric | Automated; no observer needed for reading; less susceptible to external noise. | Indirect estimation of SBP/DBP; proprietary algorithms vary and are often unpublished; accuracy issues in specific populations (AF, arterial stiffness, shock). | Calibration against auscultatory sphygmomanometry is required |

## Development Status of Automated K-sound Devices 
Given the respective advantages and limitations of the auscultatory and oscillometric blood pressure measurement methods, considerable research efforts have been directed toward developing more advanced and automated approaches. Among these, automated K-sound detection technology has emerged as a promising solution to meet this clinical need. The automation of K-sound detection addresses several critical clinical needs simultaneously. First, it preserves the physiological accuracy of the auscultatory method while eliminating the requirement for specialized operator training20. Second, automated systems can provide consistent, reproducible measurements that are not subject to human perception variability or fatigue21 22. Third, these systems can incorporate advanced signal processing techniques to enhance detection of weak or masked K-sounds that might be missed by human observers23. Moreover, it provides direct physiological measurements of BP, thereby offering improved fidelity and reliability, particularly under challenging clinical conditions24.

The quest for more reliable and objective BP measurement has driven extensive research and development of automated devices based on K-sounds. This effort includes advancements in sensor technologies, and the development of refined algorithms for detecting and interpreting these sounds

### Sensor technology and K-sound Acquisition
The accurate capture of K-sounds is the foundational step for any automated auscultatory system. To achieve this, researchers have investigated various sensor modalities, evolving from adaptations of conventional acoustic instruments to the use of novel materials and innovative designs.
Many automated K-sound systems utilize miniature microphones or electronic stethoscopes integrated within or adjacent to the BP cuff24. These sensors aim to replicate the function of a clinician's stethoscope by converting the acoustic energy of K-sounds into electrical signals. For example, Pan et al.25 utilized two electronic stethoscopes-one positioned under the cuff and another outside of it-to collect K-sound data for a deep learning model. Commercially available devices such as the InBody BPBIO480KV and the KOROT V2 Doctor integrate electronic stethoscopes within the cuff assembly and often provide clinicians with features like audible playback or visual display of detected sounds20 26. Despite their practicality, microphone-based systems are often sensitive to ambient noise and require careful acoustic coupling to the skin to ensure signal quality.

Polyvinylidene Fluoride(PVDF) is a flexible, biocompatible piezoelectric polymer that has been effectively utilized as a contact microphone for K-sound acquisition. Xiong et al.27 developed a device featuring a 1.4 × 1.4 cm PVDF film sensor with a capacitance of 700 pF, which was mounted over the brachial artery. The flexibility of PVDF allows for good conformity to the arm's curvature, potentially improving signal acquisition. Research has also explored alternative piezoelectric materials, such as lead zirconate titanate (PZT) ceramics and novel flexible piezoelectrets28. PZT offers high piezoelectric coefficients but is inherently rigid. In contrast, flexible piezoelectrets-consist of charged polymer films with internal air cavities, allowing them to exhibit piezoelectric behavior29. These materials can be fabricated into thin, flexible patches suited for wearable applications.  Notably, they have demonstrated high sensitivity and strong electromagnetic interference (EMI) shielding in detecting a variety of physiological sounds, including K-sounds. 

### Algorithmic Approaches to K-Sound Detection and Interpretation
Essential preliminary steps in K-sound analysis involve filtering and amplification. Filtering is crucial for isolating the K-sound signals, which typically lie in a frequency range of 20-300 Hz or 20-400 Hz, from background noise and other irrelevant frequencies23,30,31. The filtered signal is then often amplified to ensure its amplitude is adequate for processing by microcontrollers or for further detailed analysis. After signal processing, several algorithms have been developed to detect K-sound events associated with SBP and DBP:
Threshold-Based Detection: This is one of the more direct approaches, aiming to mimic the human auditory detection process. SBP is typically identified as the cuff pressure at which K-sounds of sufficient amplitude first appear, and DBP as the pressure at which these sounds disappear or fall below a pre-defined threshold. In some implementations, the threshold is empirically determined based on averaged values from manual measurements. 30
Power-Based Detection: This method analyzes the signal energy or power of the K-sound signal, typically in the frequency domain, during each pulse cycle. SBP is identified at the point of a marked increase in signal power, while DBP corresponds to a substantial decrease in power between successive pulses, indicating the end of audible K-sounds.30
Morphological Analysis: Some algorithms focus on the shape (morphology) of the K-sound waveforms. The B3X algorithm, for instance, evaluates the beat-by-beat changes in the morphology of adjacent K-sound pulses by calculating their cross-correlation32. Significant changes in waveform shape can indicate the onset or cessation of true K-sounds.
Time-Frequency Analysis: Techniques such as the short-time Fourier transform (STFT) and wavelet transform are used to capture temporal changes in the frequency content of K-sound signals. Features derived from these analyses can improve the accuracy of phase identification30.
Deep Learning for K-Sound Analysis: The integration of Artificial Intelligence techniques into the analysis of K-sound represents a significant step in the evolution of automated BP monitoring.  Deep learning techniques, especially Convolutional Neural Networks (CNNs) and Recurrent Neural Networks (RNNs), have been increasingly applied to automate the analysis of K sounds. These models are capable of learning complex temporal and spectral patterns directly from raw or minimally processed signals.
CNNs are commonly used for classifying audio segments as containing K-sounds or not, as well as for extracting relevant features. Input data often take the form of spectrograms or band-pass filtered signal stacks, with the latter offering better frequency resolution and phase preservation for short-duration, low-frequency K-sounds24. CNN architectures typically consist of multiple convolutional and pooling layers; for instance, Pan et al.25 used a 3-layer CNN, while Chang et al.24 adapted ResNet-18. Training relies on labeled data, either from expert annotation or probability-based methods. The outputs-K-sound presence probabilities or classifications-are then mapped to SBP and DBP using predefined decision rules, such as identifying the first and last appearance of classified beats or minimizing error against idealized probability curves. 
RNNs, particularly Long Short-Term Memory (LSTM) networks, are well-suited for sequential K-sound data. They can model temporal dependencies across beats, making them potentially more robust in handling cases like the auscultatory gap. LSTMs can incorporate contextual patterns over time, which may improve the detection of SBP and DBP under noisy or non-standard conditions. Pan et al.25 proposed that future models could integrate domain knowledge-such as the five Korotkoff phases-via RNN-based frameworks for more direct BP estimation33.

### Key Challenges in Automated K-Sound BP Monitoring
Noise and artifact: K-sounds are low-amplitude signals that are highly susceptible to noise from environmental sources, patient movement, and internal physiological activity. Such interference can result in missed or falsely detected K-sounds, leading to inaccurate blood pressure readings. Ensuring reliable performance in noisy clinical environments and during patient movement-especially in ambulatory or home settings-requires improvements in both sensor design to reduce noise sensitivity and algorithms capable of effective noise suppression and artifact rejection.
Cardiac Arrhythmias: Enhancing the accuracy of K-sound detection and blood pressure estimation in patients with cardiac arrhythmias-such as atrial fibrillation-remains a major challenge. The irregular rhythm and variable morphology of K-sounds associated with arrhythmias can disrupt conventional algorithms, leading to reduced reliability in measurement.
Arterial Stiffness: Elevated arterial stiffness can substantially impact the performance of oscillometric algorithms by altering arterial compliance and pulse wave dynamics. In contrast, K-sound-based methods are theoretically more resilient under such conditions, as the generation of K-sounds relies less on empirical assumptions regarding arterial wall properties, which are fundamental to oscillometric techniques. However, there are limited data validating the accuracy of automated K-sound-based blood pressure monitors in individuals with increased arterial stiffness. Further studies are needed to assess their performance under these conditions.


## Motivation and Objectives
Despite substantial advances in microphone-based transduction and digital auscultation hardware, reliable automated K-sound BP measurement remains challenging in real-world settings because the clinically relevant signal is often weak and highly susceptible to measurement-condition variability, including background acoustic contamination, motion-related interference, and sensor-skin coupling instability24,25. Mechanistic evidence reported by Baranger et al. (2023), obtained using in vivo ultrafast ultrasound synchronized with stethoscope recordings, provides evidence supporting a revised mechanistic interpretation of K-sounds: the authors suggested that the clinically recorded K-sounds are more consistent with tissue-borne, shear-like vibrations transmitted through surrounding tissues and coupled to nonlinear pulse-wave dynamics, rather than compressional sound waves radiating from the brachial artery; moreover, the vibration intensity was correlated with the recorded K-sound amplitude34. This revised framework suggests that prioritizing direct arterial microvibration sensing instead of airborne acoustic pressure may reduce susceptibility to ambient acoustic noise. Building on these mechanical insights, this study investigates a novel automated BP monitoring system developed by NEXVITA TECHNOLOGY CORPORATION, which integrates a custom-designed K-Sensor and an artificial intelligence (AI)-based signal interpretation framework. 
The K-Sensor employs a semiconductor strain gauge affixed to a copper alloy base to capture arterial wall microvibrations associated with K-sound. Unlike microphone-based systems, this sensor design is inherently resistant to ambient acoustic noise and is capable of enhancing intravascular hemodynamic signals. By minimizing sensitivity to environmental and physiological artifacts, the system directly addresses the signal degradation issue common in real-world settings, particularly in ambulatory or home-based monitoring scenarios.
To further improve the reliability of K-sound detection, a deep learning model based on a 2D Convolutional Neural Network (ResNet50V2) was trained using waveform images generated from the K-Sensor. This AI-based approach may also offer improved tolerance to beat-to-beat variability, suggesting possible resilience in the context of arrhythmic cardiac rhythms.
Furthermore, unlike oscillometric algorithms-which are known to be sensitive to changes in arterial compliance-K-sound-based measurements rely on the physical manifestation of arterial wall vibrations during pressure deflation. Theoretically, this modality is less affected by arterial stiffness. Although clinical validation in such populations remain limited, the K-Sensor automated BP devices focus on waveform-level detection may improve BP estimation accuracy in individuals with altered vascular properties. 
The primary objective of this study is to compare the performance of the K-Sensor-based automated BP monitor with that of a conventional oscillometric device and the current non-invasive gold standard, the auscultatory method. This comparison aims to evaluate the agreement, accuracy, and potential clinical applicability of the proposed system across diverse user conditions.



## Hypothesis 
We hypothesize that in patients with atrial fibrillation or at high risk of ASCVD, the automated K-Sensor-based blood pressure monitor demonstrates better correlation and agreement with the auscultatory method-the current noninvasive clinical gold standard-compared to conventional oscillometric blood pressure devices. This is based on the premise that K-sound-based measurement, which directly captures arterial wall vibrations, is less affected by the irregular pulse intervals of arrhythmias and altered vascular compliance associated with advanced cardiovascular pathology.


